Oral anticoagulants

### 2021-01-15 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

handlers(global = TRUE)
handlers(
  list(
    handler_progress(
      format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
      width = 60,
      complete = "+"),
    handler_beepr(finish   = "wilhelm",
                  interval = 2.0)
  )
)

@@

## Function
# Transforming data to be bound beweent a lower and upper limit http://www.maths.bristol.ac.uk/R/web/packages/fable/vignettes/transformations.html
scaled_logit <- function(x, lower=0, upper=1){
  log((x-lower)/(upper-x))
}
inv_scaled_logit <- function(x, lower=0, upper=1){
  (upper-lower)*exp(x)/(1+exp(x)) + lower
}
my_scaled_logit <- fabletools::new_transformation(scaled_logit, inv_scaled_logit)

@@

# Modifying functions to model my_scaled_logit(n, 0, 100) as using proportion data
fableModels <- function(data){
  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}

  data %>%
    mutate(datename = yearmonth(datename)) %>%
    model(trend_model1 = TSLM(my_scaled_logit(n, 0, 100) ~ trend()),#time series linear model
          trend_model2 = TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
          ets1 = ETS(my_scaled_logit(n, 0, 100) ~ trend()),
          ets2 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A")),
          ets3 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("M"), restrict = FALSE),
          arima = ARIMA(my_scaled_logit(n, 0, 100), stepwise = FALSE, approximation = FALSE),
          comb1 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend()),
                                    ETS(my_scaled_logit(n, 0, 100) ~ trend())),
          comb2 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
                                    ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A"))),
          stl_dcmp1 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          stl_dcmp2 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend() + season(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          s_naive = SNAIVE(my_scaled_logit(n, 0, 100)))
}

@@

prophetModels <- function(data){
  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}

@@

  # CV accuracy for fableModels() and prophetModels()

@@

  p <- progressr::progressor(along = regions)

  fableCV <- function(data){ # Return CV model accuracy for fableModels()
    x <- data$regional_unit

@@

    data_tr <-
      data %>%
      select(regional_unit, datename, n) %>%
      mutate(datename = yearmonth(datename)) %>%
      fill_gaps() %>%
      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
      stretch_tsibble(.init = init, .step = step)

    data_tr %>%
      fableModels() %>%
      forecast(h = cv_dist) %>%
      accuracy(data_test)

    p()
  }

  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
    x <- data$regional_unit

@@

    data_trn %>% 
      prophetModels() %>%
      forecast(h = cv_dist) %>%
      accuracy(data_test)

    p()
  }

  prophet_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~prophetCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("prophetModels() complete")

  # Fable models will run using plan(multisession), but need to be run as below
  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
  # generated
  fable_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("fableModels() complete")

@@

  fable_fit <-
    future_map_dfr(.x = regions,
                   .f = ~fableModels(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

  prophet_fit <-
    future_map_dfr(.x = regions,
                   .f = ~prophetModels(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

```{r, health-board-modelling}
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))

oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

* 724.044 seconds with multisession prophetModels()
* 418.410 seconds with neur_net removed 2021-01-11

@@

```{r, gp-cluster-modelling}
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))

@@

plan(cluster, workers = 8)
system.time(fable_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~fableModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~prophetModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
plan(sequential)

>>>>

# handlers(global = TRUE)
# handlers(
#   list(
#     handler_progress(
#       format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
#       width = 60,
#       complete = "+"),
#     handler_beepr(finish   = "wilhelm",
#                   interval = 2.0)
#   )
# )

@@

## Function
# Transforming data to be bound beweent a lower and upper limit http://www.maths.bristol.ac.uk/R/web/packages/fable/vignettes/transformations.html
scaled_logit <- function(x, lower=0, upper=1){
  log((x-lower)/(upper-x))}
inv_scaled_logit <- function(x, lower=0, upper=1){
  (upper-lower)*exp(x)/(1+exp(x)) + lower}
my_scaled_logit <- fabletools::new_transformation(scaled_logit, inv_scaled_logit)

@@

# Modifying functions to model my_scaled_logit(n, 0, 100) as using proportion data
fableModelsBound <- function(data){
  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}

  data %>%
    mutate(datename = yearmonth(datename)) %>%
    model(trend_model1 = TSLM(my_scaled_logit(n, 0, 100) ~ 
                                trend()),#time series linear model
          trend_model2 = TSLM(my_scaled_logit(n, 0, 100) ~ 
                                trend() + season("year")),
          ets1 = ETS(my_scaled_logit(n, 0, 100) ~ trend()),
          ets2 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A")),
          ets3 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("M"), 
                     restrict = FALSE),
          arima = ARIMA(my_scaled_logit(n, 0, 100), 
                        stepwise = FALSE, 
                        approximation = FALSE),
          comb1 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend()),
                                    ETS(my_scaled_logit(n, 0, 100) ~ trend())),
          comb2 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ 
                                           trend() + season("year")),
                                    ETS(my_scaled_logit(n, 0, 100) ~ 
                                          trend() + season("A"))),
          stl_dcmp1 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ 
                                                trend(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          stl_dcmp2 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ 
                                                trend() + season(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          s_naive = SNAIVE(my_scaled_logit(n, 0, 100)), .safely = TRUE)
}

@@

prophetModelsBound <- function(data){
  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}

@@

  # CV accuracy for fableModelsBound() and prophetModelsBound()

@@

  # p <- progressr::progressor(along = regions)

  fableCV <- function(data){ # Return CV model accuracy for fableModelsBound()
    x <- data$regional_unit

@@

    data %>%
      select(regional_unit, datename, n) %>%
      mutate(datename = yearmonth(datename)) %>%
      fill_gaps() %>%
      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
      stretch_tsibble(.init = init, .step = step) %>% 
      fableModelsBound() %>%
      forecast(h = cv_dist) %>%
      accuracy(data_test)

    # p()
  }

  prophetCV <- function(data){# Return CV model accuracy for prophetModelsBound()
    x <- data$regional_unit

@@

    data_trn %>% 
      prophetModelsBound() %>%
      forecast(h = cv_dist) %>%
      accuracy(data_test)

    # p()
  }

  prophet_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~prophetCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("prophetModelsBound() complete")

  # Fable models will run using plan(multisession), but need to be run as below
  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
  # generated
  fable_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("fableModelsBound() complete")

@@

  fable_fit <-
    future_map_dfr(.x = regions,
                   .f = ~fableModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

  prophet_fit <-
    future_map_dfr(.x = regions,
                   .f = ~prophetModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

```{r, health-board-modelling}
plan(multisession)
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

* 724.044 seconds with multisession prophetModelsBound()
* 418.410 seconds with neur_net removed 2021-01-11

@@

```{r, gp-cluster-modelling}
plan(multisession)
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

plan(cluster, workers = 8)
system.time(fable_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
plan(sequential)
